Palomar 5 Gaps

### 2024-09-17 paper/main.tex
updated impact time graph

\documentclass[draft]{aa}

@@

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth, trim=20 0 15 0]{monte-carlo-009-pouliasis2017pii-GCNBody-2000-milisigma-50-noisefactor-20-boxcarindexlength-shifted-0.png}
    \caption[]{A comparison between the vanilla and full simulations. This showcases our gap detection method, in which the 2D maps in \textit{tail coordinates} are inspected, and their 1D marginalized density distributions are compared quantitatively. The $x'$ coordinate indicates distance from the center of mass of Pal5 along it's orbit. The two profiles are subtraced in locations where the signal is above the noise threshold, and locations that are more that are underdense by 2-$\sigma$ are highlighted with vertical blue lines, and labeled \textit{gap candidate}. This also showcases the limitation in this 1D profile method since a very skinny and oblique gap is present, whose signal is washed out from marginalizing.}
    \label{fig:profiles}
    \end{figure*}

>>>>

\documentclass{aa}

@@

  \begin{figure*}
    \centering
    \includegraphics[width=\linewidth, trim=20 0 15 0]{monte-carlo-009-pouliasis2017pii-GCNBody-2000-milisigma-5-noisefactor-20-boxcarindexlength-shifted-0.png}
    \caption[]{A comparison between the vanilla and full simulations. This showcases our gap detection method, in which the 2D maps in \textit{tail coordinates} are inspected, and their 1D marginalized density distributions are compared quantitatively. The $x'$ coordinate indicates distance from the center of mass of Pal5 along it's orbit. The two profiles are subtraced in locations where the signal is above the noise threshold, and locations that are more that are underdense by 2-$\sigma$ are highlighted with vertical blue lines, and labeled \textit{gap candidate}. This also showcases the limitation in this 1D profile method since a very skinny and oblique gap is present, whose signal is washed out from marginalizing.}
    \label{fig:profiles}
    \end{figure*}
